Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-20 VMCAI-revised-version/final.tex
AF: prouver, si possible, les deux autres résilience

For strongly compatible WSTS,
$\pred^{\leq k}(\Safe) = \mathop{\uparrow} \pred^{\leq k}(\Safe)$
when $\Safe = \mathop[\uparrow}(\Safe)$. 
$\mathop{\uparrow} \pred^{\leq k}(\Safe)$
$k_min$ such that 
$\pred^{\leq k_{min}}(\Safe) = \pred^{*}(\Safe) $

@@

\begin{proof}
The resilience problem can be reformulated as 
$\Bad \subseteq  \pred^*(\Safe)$ that is equivalent to $\Bad \cap (S \setminus \pred^*(\Safe)) = \emptyset$.
The set $\pred^*(\Safe)$ is upward-closed, since $\Safe$ is upward-closed. Since $\mathscr{S}=(S,\rightarrow, \leq)$ is $\pred$-basis-effective, we can compute a basis of $\pred^*(\Safe)$.
Since the wqo is ideally-effective, we can compute the intersection of
$\Bad$
and
$S \setminus \pred^*(\Safe)$,
which are both downward-closed, and test if this intersection is empty or not. Hence, the resilience problem is decidable. \qed\end{proof} 
%%%%%%%
\alain{prouver, si possible, les deux autres résilience}

@@

>>>>

@@

\begin{proof}
The resilience problem can be reformulated as 
$\Bad \subseteq  \pred^*(\Safe)$ that is equivalent to $\Bad \cap (S \setminus \pred^*(\Safe)) = \emptyset$.
The set $\pred^*(\Safe)$ is upward-closed, since $\Safe$ is upward-closed. Since $\mathscr{S}=(S,\rightarrow, \leq)$ is $\pred$-basis-effective, we can compute a basis of $\pred^*(\Safe)$.
Since the wqo is ideally-effective, we can compute the intersection of
$\Bad$
and
$S \setminus \pred^*(\Safe)$,
which are both downward-closed, and test if this intersection is empty or not. Hence, the resilience problem is decidable. \qed\end{proof} 
%%%%%%%
\alain{prouver, si possible, les deux autres résilience}
Strong compatibility implies furthermore the decidability
of {\sc $k$-resilience} and {\sc bounded-resilience}.

@@

\begin{proof}
For strongly compatible WSTS,
$\pred^{k}(\Safe) = \mathop{\uparrow} \pred^{k}(\Safe)$,
and hence
$\pred^{\leq k}(\Safe) = \mathop{\uparrow} \pred^{\leq k}(\Safe)$,
when $\Safe = \mathop{\uparrow} \Safe$. 
Since $\mathscr{S}=(S,\rightarrow, \leq)$ is $\pred$-basis-effective, we can compute a basis of $\mathop{\uparrow} \pred^{\leq k}(\Safe) = \pred^{\leq k}(\Safe)$.
Like above, we can test if the intersection of $\Bad$
and
$S \setminus \pred^{\leq k}(\Safe)$ is empty or not, hence {\sc $k$-resilience} is decidable.
To decide {\sc Bounded resilience}, we check {\sc $k$-resilience}
starting with $k=0$ until we find some $k_0$ such that either {\sc $k_0$-resilience} holds,
either $\pred^{\leq k_0}(\Safe) = \pred^{\leq k_0+1}(\Safe)$, whichever comes first.
The convergence of $(\pred^{\leq k}(\Safe) )_{k\in\N}$ guarantees the latter eventually happens.
\end{proof}
